\begin{rubric}{Invited Talks}


% http://icis.ucdavis.edu/?tribe_events=workshop-the-social-life-of-medical-data
\text{Fish, A., \textbf{Clark, D.}, Dumit, J., Fallon, K., \& Irani, L. (2015,
    June). The Challenges of Research Design: Tools and Interventions. Invited
    roundtable at The Social Life of Medical Data, Davis, CA.  }

\text{}

% http://icis.ucdavis.edu/?page_id=329
\text{Auriti, E., Borgman, C., \textbf{Clark, D.}, Anderson, N., Stahmer, C., Lippman,
    A. (2014, December). Perspectives on Data Sharing Across the Research
    Enterprise. Invited panel at Data Rights \& Data Wrongs, Davis, CA. }

\text{}

\text{\textbf{Clark, D.} (2014, December). Collaborative training in
    RStudio/Rmarkdown. Training delivered at the BITSS Annual Meeting. }

\text{}

\text{\textbf{Clark, D.}, Nelson, A., Ram, K., \& Koy, K. (2014, June). Data Science
    Meets Social Science. Invited Roundtable (moderator).}

\text{}

\text{Monroe, I., \& \textbf{Clark, D.} (2013, September). \emph{Saving Oceans
        with Social and Behavioral Changes.} Invited talk at the Hive Big Data
    Think Tank, San Francisco, CA.}

\text{}

\text{\textbf{Clark, D.}, Reinholz, D., Farjadi, R., Cohen, S., and Ranney, M.A.
    (2011, October).  \emph{Understanding and Changing Cognitions and Behaviors
        About Global Warming} Seminar presented to UC Berkeley DeCal:
    Behavioral Change + Technology, Berkeley, CA.}

\text{}

\text{Ranney, M. A., \textbf{Clark, D.}, and Reinholz, D. (2011, October).
    \emph{``Rick Perry, methane, \& an early hominid enter a saloon\ldots'':
    Climate change, evolution, (anti-)knowledge, math, and geopolitics.}
    Invited colloquium for the Institute of Cognitive and Brain Sciences,
    University of California, Berkeley.}

\text{}

\text{\textbf{Clark, D.}, Reinholz, D., Farjadi, R., and Ranney, M. A. (2011,
    September). \emph{Towards an informed populace: two
    approaches for addressing faulty prior knowledge.} Seminar
    presented to the UC Berkeley Cognitive Coalition (CoCoa), Berkeley,
    CA.}

\text{}

\text{\textbf{Clark, D.,} Reinholz, D., Felipe, J., Cain, A., Beale, M.,
    Lazaris, A., Qi, H., Fong, J., Farjadi, R., \& Ranney, M. A. (2011, April).
    \emph{The “Goldilocks Asymmetry” of Energy Transfer Rates: An Experimental
        Intervention Toward Saving Us from Global Warming.}
    Research in Cognition and Mathematics Education
    (RCME) proseminar, Berkeley, CA.}

\text{}

\text{\textbf{Clark, D.} (2009, October). \emph{Python data discussion
        (HDF5, R, Numpy)}. UC Berkeley Python 4 Science seminar, Berkeley, CA.}

\text{}

\text{\textbf{Clark, D.} (2009, April). \emph{Learning numerical
    information: A memory systems approach to educational strategy.}
    USF Undergraduate Neuroscience Seminar, San Francisco, CA.}

\text{}

\text{\textbf{Clark, D.} (2001, April). \emph{More is better: Predicting word
    memory with prefrontal activation.} MIT Speech Communication Group
    Seminar Series, Cambridge, MA.}

\end{rubric}
