\begin{rubric}{Other Experience}

\entry*[2013--present] \emph{Data Scientist, UC Berkeley D-lab}
    \par Tasked with building technical and cultural infrastructure to render
    data science more accessible to social scientists. Tasks include curriculum
    development, instruction, and technology specification and evaluation.

\entry*[2012--present] \emph{Chief Scientist, Oroeco}
    \par Ruby on Rails project to scaffold climate-relevant behavioral change.
    Responsible for components of the web application, and developing approaches
    to systematically analyze user behaviors---in particular the results of
    interventions.

\entry*[2007--present] \emph{Feldenkrais Teacher, Consultant}
    \par  Hands-on and verbal instruction to improve students' movement
    abilities, often in a rehabilitative context.
    % more comfortably, efficiently, powerfully or other good things. 
    Completed 4-year training. Weekly class at YMCA from 2007--2011. Various
    dance workshops in 2012. Full day FGNA conference presentation in 2012.

% June 2009 - July 2011
%\entry*[2009--2011] \emph{Feldenkrais Teacher, YMCA}
%    \par Verbally guided instruction to improve students' ability to
%    move more comfortably, efficiently, powerfully or other good things.

% June 2004
\entry*[2004--2013] \emph{Web Service Developer, Contractor / KeepOpen.com}
    \par Using technologies like HDF5, Zope and Google Maps to implement services
    for community events management, small businesses, resource sharing, etc.
    Patent development.

% May 2006 - May 2007
\entry*[2006--2007] \emph{Principal Scientist, Entrieva}
    \par Developed multiple reporting frameworks using relational database and
    hierarchical HDF5 design.  Analysis and reduction of code to basic
    mathematical notation.  Domain expert in computational linguistics and
    semantic web technology.  Primary responsibility: "Do good stuff."

% February 2006 - April 2006 
\entry*[2006] \emph{Programmer, Wandell Lab / Stanford}
    \par Developing a brain imaging repository from scratch using REST design
    and HDF5 data storage using PyTables.  Clients include a Matlab /
    Java program, a web browser and mounting via WebDAV.  Server
    written using mod_python.  NumPy used for matrix operations.

% January 2005 - February 2006
\entry*[2005--2006] \emph{Programmer/Analyst, Davachi Lab / NYU}
    \par Variety of novel analyses of subsequent memory fMRI data collected
    during free viewing of a movie.  Working with an undergraduate researcher in
    developing analysis of associated eye-tracking data.  Duties also include
    development, automation and technical support of other analyses being done
    in the lab.

% January 2003 - May 2004
\entry*[2003--2004] \emph{Various Independent Activities}
\begin{compactitem} 
    \item Business plan competitions:  MIT Sloan (semi-finalist) and Harvard
        (runner up, \$4000 as in-kind services). 
    \item Classical opera and contemporary performance art.
    \item Real estate agent. 
    \item Extensive travel. 
    \item Organic farming, straw bale and mud brick house construction. 
    \item Organizer and attendee for various holistic bodywork training sessions. 
\end{compactitem}

% April - December 2002
\entry*[2002] \emph{Programmer/Analyst, Massachusetts General Hospital}
    \par Supported complex analyses in a flagship brain imaging research center.
    Included implementing novel techniques for statistics and visualization,
    integrating fMRI, sMRI and MEG.

\end{rubric}
