\begin{rubric}{Positions}

\entry*[2016--present] \emph{Research Scientist, Kennedy Krieger Insititute}
\par Developing and assessing interventions for children with developmental
challenges. Data include TMS, fMRI, physiologic and motor measures, and
cognitive and clinical testing. Extensive secondary usage of existing data
sources.

\entry*[2013--2016] \emph{Data Scientist, UC Berkeley Data-intensive Social
    Science Lab (D-Lab)}
\par Big Data Compute lead. Providing broad support across campus for
computaionally intensive social science. Includes training, consulting, data
management, and software development for internal programs. “Data Czar” for
Berkeley's EdX (Massive Online Open Course) program. Work with research
computing support to make standard (virtual) computing environments available
for training and collaborative research.

\entry*[2014--2016] \emph{Fellow, UC Berkeley Institute for Data Science
    (BIDS)}
\par Selected via a highly competitive application process to be a fellow in the
Moore--Sloan initiative to improve computational scientific practice. My focus
is on the collection and management of social data, inclusive of non-technical
concerns like privacy and security.

\entry*[2014, 2015] \emph{Lecturer, UC Berkeley School of Information} 
\par Masters in Data Science (2014): Introduction to machine learning course
that my students have said is the most challenging, most rewarding course in
the program. Hacking Measurement (2015): Project-based introduction to sensor,
mobile, and structured text mining for social, health and environmental data.

\entry*[2012--2014] \emph{Chief Scientist, Oroeco}
\par Ruby on Rails project to scaffold climate-relevant behavioral change.
Responsible for components of the web application, and developing approaches
to systematically analyze user behaviors---in particular the results of
interventions.

\entry*[2007--present] \emph{Feldenkrais Teacher, Consultant}
\par  Hands-on and verbal instruction to improve students' movement
abilities, often in a rehabilitative context.
% more comfortably, efficiently, powerfully or other good things. 
Completed 4-year training. Have taught weekly classes, various dance
workshops, and private lessons. Full day FGNA conference presentation in
2012.

\entry*[2004--2013] \emph{Web Service Developer, Contractor / KeepOpen.com}
    \par Using technologies like HDF5, Zope and Google Maps to implement services
    for community events management, small businesses, resource sharing, etc.
    Patent development.

% May 2006 - May 2007
\entry*[2006--2007] \emph{Principal Scientist, Entrieva}
    \par Developed multiple reporting frameworks using relational database and
    hierarchical HDF5 design.  Analysis and reduction of code to basic
    mathematical notation.  Domain expert in computational linguistics and
    semantic web technology.  Primary responsibility: “Do good stuff.”

% February 2006 - April 2006 
\entry*[2006] \emph{Programmer, Wandell Lab / Stanford}
    \par Developing a brain imaging repository from scratch using REST design
    and HDF5 data storage using PyTables.  Clients include a Matlab /
    Java program, a web browser and mounting via WebDAV.  Server
    written using mod_python.  NumPy used for matrix operations.

% January 2005 - February 2006
\entry*[2005--2006] \emph{Programmer/Analyst, Davachi Lab / NYU}
    \par Variety of novel analyses of subsequent memory fMRI data collected
    during free viewing of a movie.  Working with an undergraduate researcher in
    developing analysis of associated eye-tracking data.  Duties also include
    development, automation and technical support of other analyses being done
    in the lab.

% January 2003 - May 2004
\entry*[2003--2004] \emph{Various Independent Activities}
\begin{compactitem}
    \item Business plan competitions:  MIT Sloan (semi-finalist) and Harvard
        (runner up, \$4000 as in-kind services)
    \item Classical opera and contemporary performance art
    \item Real estate agent
    \item Extensive travel
    \item Organic farming, straw bale and mud brick house construction
    \item Organizer and attendee for various holistic bodywork training sessions
\end{compactitem}

% April - December 2002
\entry*[2002] \emph{Programmer/Analyst, Massachusetts General Hospital}
    \par Supported complex analyses in a flagship brain imaging research center.
    Included implementing novel techniques for statistics and visualization,
    integrating fMRI, sMRI and MEG.
\end{rubric}
