\begin{rubric}{Presentations}

% Xmobile / Behav Meas + Change seminar - http://xmobile.berkeley.edu/seminar

\text{\textbf{Clark, D.} (2013, June). \emph{Combating Climate Change With
        Education And Incentives For Individuals.}
    Poster session presented at the Garrison Institute Climate, Mind, and
    Behavior Sympusium, Garrison, NY.}

\text{}

\text{Ranney, M.A., \textbf{Clark, D.}, \& Reinholz, D. (2012, November).
    \emph{Enhancing Global Warming Understanding and Acceptance with Veridical
        Statistics and Mechanistic Information.} Poster session presented at the
    Behavior, Energy \& Climate Change Conference, Sacramento, CA.}
\text{}

\text{\textbf{Clark, D.} (2012, September). \emph{Getting Precise With Our Complex Brains.}
    Full-day workshop presented at the Feldenkrais Method Annual Conference, San Mateo, CA.}

\text{}

\text{Ranney, M.A., \textbf{Clark, D.}, Reinholz, D., Crain, M., \& Gillingham, D.
    (2012, October). \emph{How Journalists and Educators Can Help Preserve Earth’s
    Biosphere by Improving Numeracy and Scientific Informativeness.} Paper
    presented at the annual meeting of the National Numeracy Network, New York
    City.}

\text{}

\text{Ranney, M. A., \textbf{Clark, D.}, Reinholz, D. L., Farjadi, R., Beale,
    M., \& Wilson, J. (2012, May). \emph{Changing People’s Incorrect Global Warming Beliefs
    with True Statistics and Mechanistic Information.} Paper presented at the The
    Association for Psychological Science’s 24th Annual Convention, Chicago,
    IL.}

\text{}

\text{\textbf{Clark, D.},  Stoloff, R., \& Ivry, R. B. (2011, September).
\emph{The neural signature of free vs. forced hand choice.} Poster session
presented at the 41st annual meeting of the Society for Neuroscience,
Washington, DC.}

\text{}

\text{\textbf{Clark, D.}, Reinholz, D., Cohen, S., Walket, B., \& Ranney, M. A.
(2011, August). \emph{Overcoming Climate Change Biases by Teaching the
    “Goldilocks Asymmetry” of Energy Transfer Rates: A Cognitive-Strategy
    Attempt to Save Us Organisms.} Paper presented at the Eighteenth Annual
Meeting of the Cognitive Science Association for Interdisciplinary Learning,
Hood River, OR.}

\text{}

\text{\textbf{Clark, D.}, Reinholz, D., Goldwasser, L., \& Ranney, M. A. (2011,
April) \emph{Can Teaching the "Goldilocks Asymmetry" About Energy Transfer Rates
Save Us Organisms? An Experiment on Climate Change Instruction.} Paper presented
at the Graduate School of Education (GSE) Research Day, Berkeley, CA.}
% Which nth GSE research day was this?

\text{}

\text{Ghosh, S., Burns, C., \textbf{Clark, D.}, Gorgolewski, K., Halchenko, Y.,
    Madison, C., Tungaraza R., \& Millman J. (2010). \emph{Nipype: Opensource
    platform for unified and replicable interaction with existing
    neuroimaging tools.} Poster session presented at the 16th Annual Meeting of the
    Organization for Human Brain Mapping.}
% Where was this? What month?

\text{}

\text{\textbf{Clark, D.} (2010, April). \emph{Surprising Feedback And Fallible 
    Metacognition: Beliefs Versus Facts in Real-World Numerical Estimation and
    Recall.} Paper presented at the Graduate School of Eduction (GSE) Research
    Day, Berkeley, CA.}

\text{}

% What month was this? Do I do the month here?
\text{\textbf{Clark, D.}, Ivry, R.B. (2009). \emph{Hemispheric Asymmetry in fMRI 
    Activation with Direct or Indirect Cueing of Sequential Movements.} Poster
    session presented at the 19th Annual Meeting of the Neural Control of
    Movement Abstracts, Waikiloa, HI.}

\text{}

% What month was this?
\text{Furman, O., Hasson, U., \textbf{Clark, D.}, Dudai, Y., Davachi, L. (2006).
    \emph{Neural correlates of long-term memory formation under continuous
    real-life viewing conditions.} Poster session presented at the 12th
    Annual Meeting of the Organization for Human Brain Mapping.}

\text{}

% month?
\text{O'Kane, G., \textbf{Clark, D.}, Insler, R., \& Wagner, A. D. (2003).
    Generalized
    semantic repetition priming in left inferior prefrontal cortex. \emph{Abstracts of
        the Cognitive Neuroscience Society, 10,} 73.}

\text{}

\text{\textbf{Clark, D.}, Rhee, J., \& Wagner, A. D. (2001).  Prefrontal
    activation during
    phonological encoding predicts subsequent memory. \emph{Abstracts of the Cognitive
    Neuroscience Society, 8,} 58.} 

\text{}

\text{Rhee, J., \textbf{Clark, D.}, Casasanto, D., Ullman, M., Wagner, A., \&
    Pinker, S.
    (2001).  Neural substrates of English past tense generation. \emph{Abstracts of
    the Cognitive Neuroscience Society, 8,} 131.}

\text{}

\text{\textbf{Clark, D.}, \& Wagner, A. D. (2001). A role for phonological
    working memory: Building representations for novel word stimuli. \emph{Society
    for Neuroscience Abstracts, 27.}}

\end{rubric}
